---
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
resource_files:
- _site.yml
- single_words.Rproj
runtime: shiny
title: "Single Word Norms"
---

<p>

```{r setup, echo = FALSE, warning=FALSE, include=FALSE}
#load the libraries
library(DT)
library(MOTE)
library(shiny)
options(scipen = 999)

#deal with the data for the var table
singlewordtable = read.csv("SingleWordTab.csv")
singleworddata = read.csv("single_word.csv")

singlewordtable$Minimum = c(apa(apply(singleworddata[ , 2:9], 2, min, na.rm = T), 2), 
                            NA, apa(apply(singleworddata[ , 11:15], 2, min, na.rm = T), 2))
singlewordtable$Maximum = c(apa(apply(singleworddata[ , 2:9], 2, max, na.rm = T), 2), 
                            NA, apa(apply(singleworddata[ , 11:15], 2, max, na.rm = T), 2))
singlewordtable$M = c(apa(apply(singleworddata[ , 2:9], 2, mean, na.rm = T), 2), 
                      NA, apa(apply(singleworddata[ , 11:15], 2, mean, na.rm = T), 2))
singlewordtable$SD = c(apa(apply(singleworddata[ , 2:9], 2, sd, na.rm = T), 2), 
                       NA, apa(apply(singleworddata[ , 11:15], 2, sd, na.rm = T), 2))
```

On this page, you will find information about our single word norms used in our projects. We have split our single and paired word norms into two separate databases to speed database processing time for the user. Single word norms (i.e., variables) are concept information that are only tied to a single concept, such as imaginability, concreteness, or number of phonemes. This dataset includes all cues, targets, and features from the Buchanan et al. semantic word-pair norms (2013) and our extension project, which can be found on [OSF](https://osf.io/cjyzw/) and [GitHub](https://github.com/doomlab/Word-Norms-2). When downloading the applications to run locally on RStudio, please be sure to download the entire folder on our [GitHub repository](https://github.com/doomlab/shiny-server/tree/master/wn_single).

### Variable Table

You can view the complete variable table that lists the variables, their descriptions, min, max, mean, and standard deviation calculated dynamically from the current dataset. Norms are taken from the University of South Florida Free Association Norms (Nelson, McEvoy, & Schreiber, 2004) and the English Lexicon Project (Balota et al., 2007).

```{r single_var_table, echo=FALSE}
ui <- fluidPage(
  #titlePanel("Single Words Variable List"),
  DTOutput('tbl'))
  
server <- function(input, output) {
  output$tbl = renderDT(
    singlewordtable, 
    extensions = 'Responsive',
    options = list(
      dom = 'tp'
    ),
    rownames = FALSE
    
  )
}

shinyApp(ui, server, options = list(height = 600))
```

<br>

### View and Search the Words

You can use the Shiny app provided below to view all the words and their information. Use the search filters at the top of the table to pick specific ranges of variables or categories.

```{r single_words, echo = FALSE}
ui <- fluidPage(
   #titlePanel("Single Word Norms"),
   div(style = 'overflow-x: scroll', DTOutput("singletable"))
   ) #fluidpage

server <- function(input, output) {
   
   output$singletable <- renderDT({
     
     datatable(singleworddata,
               filter = 'top',
               rownames = FALSE,
               extensions = 'Buttons',
               options = list(
                 dom = 'rtpB',
                 buttons = c('copy', 'csv', 'excel')
               ) #close options
               ) #close data table 
     
   }) #close render DT
      
}

# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 550))
```

<br>

### Download the Data

You can download the csv file of the single word information [here](https://github.com/doomlab/shiny-server/blob/master/wn_single/single_word.csv).



