---
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
resource_files:
- _site.yml
- lab_table.Rproj
runtime: shiny
        
---
<p>

```{r setup, echo = FALSE, warning=FALSE, include=FALSE}
#libraries
library(shiny)
library(DT)
library(MOTE)
library(reshape)
library(plyr)
library(ggplot2)
options(scipen = 999)

overall_lab = read.csv("lab_table.csv")

cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))
```

### LAB: Linguistic Annotated Bibiolography

Purpose Statement: 

This article and associated website presents the Linguistic Annotated Bibliography (LAB) as a searchable web portal to quickly and easily access reliable database norms, related programs, and variable calculations. These publications were coded by language, number of stimuli, stimuli type (i.e., words, pictures, symbols), keywords (i.e., frequency, semantics, valence), and other useful information. This tool not only allows researchers to search for the specific type of stimuli needed for experiments, but also permits the exploration of publication trends across 100 years of research. Details about the portal creation and use are outlined, as well as various analyses of change in publication rates and keywords. In general, advances in computational power have allowed for the increase in dataset size in the recent decades, in addition to an increase in the number of linguistic variables provided in each publication.

If you would like to download the app to run locally, please download the entire folder at [GitHub](https://github.com/doomlab/shiny-server/tree/master/wn_lab). You can view the pre-print of this paper at [OSF](https://osf.io/h3bwx/), the main [OSF project page](https://osf.io/9bcws/), and the associated [GitHub repository](https://github.com/doomlab/Table-of-Doom).

### Help Update

We have created a [Mendeley Group](https://www.mendeley.com/community/the-lab-linguistic-annotated-bibliography/) for users to add resources or create bibliographies from the works provided in the LAB. Anyone can join the group with a Mendeley account and add documents. In order to notify us of new citations we should add to our database, please tag Erin Buchanan by leaving a note on the overview page of the group. To tag someone, simply type the at symbol @ followed by their name. If you do not want to use Mendeley, you can download a [BibTex file](https://github.com/doomlab/shiny-server/blob/master/wn_lab/LAB%20Bib.bib) of the citations in the LAB table to import into your own citation management software. [Email](mailto:buchananlab@gmail.com) suggestions of articles are also accepted. 

We take suggestions for articles that include corpora, subjective norms (i.e., participant rated), calculated norms (i.e., things like cosine or other word space model calculations), stimuli (pictures, videos, audio, ratings), linguistic software, and websites. Papers that just use norms would normally be excluded. As new updates are provided, we will continue to assess the types of columns needed for tags and add them as we go - for example, as part of the updates in the revision process, we realized that "syntax" and "accuracy" tags were useful because of the number of times listed in the notes_var column of the full dataset. 

### Versioning and Citing

Preprint citation: Buchanan, E. M., Valentine, K. D., & Maxwell, N. (2018). The LAB: Linguistic Annotated Bibliography. https://doi.org/10.31219/osf.io/h3bwx

Current version LAB Database/Shiny Application: Buchanan, E. M., Valentine, K. D., & Maxwell, N. P. (2018). LAB: Linguistic Annotated Bibliography - Shiny Application. Retrieved from http://aggieerin.com/shiny/lab_table. [![DOI](https://zenodo.org/badge/116844736.svg)](https://zenodo.org/badge/latestdoi/116844736)

Want to cite a different version? You can view our [Releases page](https://github.com/doomlab/shiny-server/releases) to see the changes we've made across time and view the associated doi with that release at [Zenodo](https://zenodo.org/badge/latestdoi/116844736). We use GitHub Releases, which automatically sync to Zenodo, to indicate updates to the project to help track versioning for this work. We expect to update with the paper updating and as users/our lab provide new information to add to the LAB. 

### Download the Data

You can download the csv file of the LAB table information [here](https://github.com/doomlab/shiny-server/blob/master/wn_lab/lab_table.csv). This file is structured such that each citation receives a line in the database, with citation information, stimuli type, language information, and tags are separated into columns. For example, each of the major tags are separated into columns and dummy coded (i.e., 0 = not included, 1 = included). This format allows for manipulation and assessment of information by variable. In the searchable option below, the data is condensed to the most common searchable information (stimuli, tag, and language). The full dataset expands this information with other notes, reference links, language Glottolog code, and BibTex citation key from our BibTex file. The Stimuli Table descriptions can be found [here](https://github.com/doomlab/shiny-server/blob/master/wn_lab/StimWordTab.csv) and Tag table descriptions can be found [here](https://github.com/doomlab/shiny-server/blob/master/wn_lab/TagWordTab.csv).

### Stimuli Table

Stimuli were coded based on the dominant description from the article (i.e., although heteronyms are words and word pairs, they were coded specifically as heteronyms). The number of stimuli presented in the appendix or database was coded with the stimuli, unless the article covered specific programs, search or experimental creation tools, which is the majority of the "other" stimuli category. Because many articles included two types of stimuli, or references to different articles where stimuli were selected from, two options for stimuli were included. Therefore, the total values for number of stimuli do not add up to the number of articles in the database because of multiple instances in articles or no stimuli for program descriptions. The table provided below indicates a description of the types of stimuli and descriptive statistics calculated from the most updated dataset. 

```{r stim_var_table, echo=FALSE}
#set up for stim var table
stimwordtable = read.csv("StimWordTab.csv")
stimworddata = overall_lab

type1 = stimworddata[ , c("no1", "type1")]
type2 = stimworddata[ , c("no2", "type2")]
colnames(type2) = c("no1", "type1")
stimworddata = rbind(type1, type2)
stimworddata = subset(stimworddata, type1 != "")
stimworddata$type1 = droplevels(stimworddata$type1)
stimworddata$type1 = factor(stimworddata$type1, 
                            levels = stimwordtable$Stimuli)

stimwordtable$N = table(stimworddata$type1)

stimwordtable$Minimum = apa(tapply(stimworddata$no1, stimworddata$type1, min, na.rm = T),2)
stimwordtable$Maximum = apa(tapply(stimworddata$no1, stimworddata$type1, max, na.rm = T),2)
stimwordtable$M = apa(tapply(stimworddata$no1, stimworddata$type1, mean, na.rm = T),2)
stimwordtable$SD = apa(tapply(stimworddata$no1, stimworddata$type1, sd, na.rm = T),2)

#app part
ui = fluidPage(
  #titlePanel("Stimuli Variable List"),
  DTOutput('tbl'))

server = function(input, output) {
  output$tbl = renderDT(
    stimwordtable, 
    extensions = 'Responsive',
    options = list(
      dom = 'tp'
    ),
    rownames = FALSE
    
  )
}

shinyApp(ui, server, options = list(height = 950))
```

### Tag Table

Keyword tags are the majority of the database, as they allow for the best understanding of trends and availability of stimuli. The table below portrays a list of tags, description of the tag, frequencies, and correlations between year and tag frequency. Each article was coded with tags based on the description of the accessible data, and one article may have multiple tags. However, due to the cumulative nature of database research, this tagging system does not mean that each article collected that particular type of data. The most common example of this distinction occurs when data was combined across sources, but presented in a new article. 

```{r tag_var_table, echo=FALSE}
#set up for tag var table
tagwordtable = read.csv("TagWordTab.csv")
tagworddata = overall_lab

tagworddata = tagworddata[ , c("accuracy","aoa","ambiguity","arousal","assoc","category",
                               "cloze","complex","concrete","confusion","context", "dist",
                               "dominate","easelearn","familiar","freq","gpc",
                               "identify","identifyld","identifyn","imageagree",
                               "imagevar", "imagine","intense","letters", "meaning",
                               "modality","morph","nameagree","orthon","pos",
                               "phonemes","phonon","prime","pronounce",
                               "rt","recall","recognition","rime","semantic",
                               "sensory","sentcomp","similar","syllables", "syntax",
                               "typical","valence","visualcomp","wordcomp","year")]

longtag = melt(tagworddata,
                   id = c("year"),
                   measured = c("accuracy","aoa","ambiguity","arousal","assoc","category",
                               "cloze","complex","concrete","confusion","context", "dist",
                               "dominate","easelearn","familiar","freq","gpc",
                               "identify","identifyld","identifyn","imageagree",
                               "imagevar", "imagine","intense","letters", "meaning",
                               "modality","morph","nameagree","orthon","pos",
                               "phonemes","phonon","prime","pronounce",
                               "rt","recall","recognition","rime","semantic",
                               "sensory","sentcomp","similar","syllables", "syntax",
                               "typical","valence","visualcomp","wordcomp"))
longtag$year = as.numeric(as.character(longtag$year))
tagwordtable$r = apa(as.matrix(by(longtag, longtag$variable, function(x) {cor(x$year, x$value, use = "pairwise.complete.obs")}))[ , 1],3, F)
tagwordtable$N = table(longtag$variable[longtag$value == 1])

#app part
ui = fluidPage(
  #titlePanel("Tag Variable List"),
  DTOutput('tbl'))

server = function(input, output) {
  output$tbl = renderDT(
    tagwordtable, 
    extensions = 'Responsive',
    options = list(
      dom = 'tp'
    ),
    rownames = FALSE
    
  )
}

shinyApp(ui, server, options = list(height = 600))
```

### View and Search The Database

You can use the Shiny app below to view all the publication entries and their information. Use the side bar to filter the dataset. As you add additional search criteria, the filter will include only items with all of the selected options. Are we missing something? Please [email](mailto:buchananlab@gmail.com) us any information you find that is incorrect or missing. We do not assume this list is complete and would love to add more data to the LAB. Please note we distilled this search to the main components (tags, language, stimuli) but the entire dataset has many columns to filter by more precise information.

```{r lab_table, echo=FALSE}
#set up for lab table
labtable = overall_lab

#clean up journal information
labtable$Full.Reference = with(labtable, paste(author, year, ref_title,
                                            ref_journal, ref_volume, 
                                            ref_page, ref_doi, sep = ". "))
#clean up the tags
labtable$Tag.List = apply(labtable[ , 21:66] == 1, 1, function(x) { toString(names(which(x))) } )

#clean up the stimuli
labtable$Stimuli.List = paste(labtable$no1, " ", labtable$type1, ", ",
                              labtable$no2, " ", labtable$type2, sep = "")

labtable$Stimuli.List = gsub("NA", "", labtable$Stimuli.List, ignore.case = F)
labtable$Stimuli.List = gsub(",\\s\\s$", "", labtable$Stimuli.List, ignore.case = F)

#language
labtable$Lang.List = paste(labtable$language, " ", labtable$notes_lang, sep = "")

ui = fluidPage(
  #titlePanel("LAB Table List"),
  sidebarLayout(
    
    sidebarPanel(
      selectizeInput("stimuli", "Select Stimuli:", 
                     choices = c(names(table(labtable$type1))), 
                     multiple = TRUE),
      
      selectizeInput("tags", "Select Tags:", 
                     choices = c(
                       "Accuracy" = "accuracy",
                       "Age of Acquisition" = "aoa",
                       "Ambiguity" = "ambiguity",
                       "Arousal" = "arousal",
                       "Association" = "assoc",
                       "Categories" = "category",
                       "Cloze Probabilities" = "cloze",
                       "Complexity" = "complex",
                       "Concreteness" = "concrete",
                       "Confusion Matrices" = "confusion",
                       "Context" = "context", 
                       "Distinctivenes" = "sdist",
                       "Dominance" = "dominate",
                       "Ease of Learning" = "easelearn",
                       "Familiarity" = "familiar",
                       "Frequency" = "freq",
                       "Grapheme-Phoneme Correspondence" = "gpc",
                       "Indentification" = "identify",
                       "Image Agreement" = "imageagree",
                       "Image Variability" = "imagevar",
                       "Imaginability" = "imagine",
                       "Intensity" = "intense",
                       "Letters" = "letters",
                       "Lexical Decision" = "identifyld",
                       "Meaning" = "meaning",
                       "Modality" = "modality",
                       "Morphemes" = "morph",
                       "Name Agreement" = "nameagree",
                       "Naming" = "identifyn",
                       "Orthographic Neighborhood" = "orthon",
                       "Part of Speech" = "pos",
                       "Phonemes" = "phonemes",
                       "Phonographic Neighborhood" = "phonon",
                       "Priming" = "prime",
                       "Pronunciation" = "pronounce",
                       "Response Latency" = "rt",
                       "Recall" = "recall",
                       "Recognition" = "recognition",
                       "Rime" = "rime",
                       "Semantic" = "semantic",
                       "Sensory" = "sensory",
                       "Sentence Completion" = "sentcomp",
                       "Similarity" = "similar",
                       "Syllables" = "syllables",
                       "Syntax" = "syntax", 
                       "Typicality" = "typical",
                       "Valence" = "valence",
                       "Visual Complexity" = "visualcomp",
                       "Word Completion" = "wordcomp"), 
                     multiple = TRUE),
      
      selectizeInput("language", "Select Language:", 
                     choices = c(names(table(labtable$language))), 
                     multiple = TRUE)
      
    ), #sidebar panel
    
    mainPanel(
      DTOutput('tbl')
    ) #close main panel
  
  )##sidebar layout
  
  )##fluidpage

server = function(input, output) {
  output$tbl = renderDT(server = FALSE, {
    
    temptable = labtable[ , (ncol(labtable)-3):(ncol(labtable))]
    
    if (!is.null(input$stimuli)) {
    for (i in 1:length(input$stimuli)) {
      temptable = temptable[grep(input$stimuli[i], temptable$Stimuli.List), ]
    }
    }
    
    if (!is.null(input$tags)) {
      for (i in 1:length(input$tags)) {
        temptable = temptable[grep(input$tags[i], temptable$Tag.List), ]
      }
    }
    
    if (!is.null(input$language)) {
      for (i in 1:length(input$language)) {
        temptable = temptable[grep(input$language[i], temptable$Lang.List), ]
      }
    }
    
    datatable(temptable, 
    extensions = 'Buttons',
    options = list(dom = 'BRtp',
                   filename = 'searchresults',
                   buttons = c('copy', 'csv', 'excel')),
    rownames = FALSE) #close datatable
  
  })
  } #close server

shinyApp(ui, server, options = list(height = 900))

```

### View the Frequency Statistics

This app allows you to view the frequencies of tags, stimuli, languages, and journals.

```{r frequencies, echo=FALSE}
#set up for frequencies
tablemain = overall_lab

##use the value column for the table below because it contains all the stimuli names
type = subset(tablemain, select = c(STUFFID, type1, type2))
longtype = melt(type, 
                 id = c("STUFFID"), 
                 measured = c("type1", "type2"))
longtype = subset(longtype, value != "")

##use the variable column for the table below because it has all the tag names

stimuli = subset(tablemain, select = c("STUFFID",
                                "accuracy","aoa","ambiguity","arousal","assoc","category",
                               "cloze","complex","concrete","confusion","context", "dist",
                               "dominate","easelearn","familiar","freq","gpc",
                               "identify","identifyld","identifyn","imageagree",
                               "imagevar", "imagine","intense","letters", "meaning",
                               "modality","morph","nameagree","orthon","pos",
                               "phonemes","phonon","prime","pronounce",
                               "rt","recall","recognition","rime","semantic",
                               "sensory","sentcomp","similar","syllables", "syntax",
                               "typical","valence","visualcomp","wordcomp"))
longstimuli = melt(stimuli,
                id = c("STUFFID"),
                measured = c("accuracy","aoa","ambiguity","arousal","assoc","category",
                               "cloze","complex","concrete","confusion","context", "dist",
                               "dominate","easelearn","familiar","freq","gpc",
                               "identify","identifyld","identifyn","imageagree",
                               "imagevar", "imagine","intense","letters", "meaning",
                               "modality","morph","nameagree","orthon","pos",
                               "phonemes","phonon","prime","pronounce",
                               "rt","recall","recognition","rime","semantic",
                               "sensory","sentcomp","similar","syllables", "syntax",
                               "typical","valence","visualcomp","wordcomp"))

longstimuli = subset(longstimuli, value > 0) 

longstimuli$variable = factor(longstimuli$variable,
                              levels = levels(longstimuli$variable), 
                              labels = c("Accuracy", "Age of Acquisition", 
                                         "Ambiguity", "Arousal",
                                         "Association", "Category", "Cloze", "Complexity",
                                         "Concreteness", "Confusion Matrices", 
                                         "Context", "Distinctness",
                                         "Dominance", "Ease of Learning", "Familiarity", 
                                         "Frequency", "Grapheme-Phoneme Correspondence", 
                                         "Indentification", "Lexical Desicion", "Naming",
                                         "Image Agreement", "Image Variability", 
                                         "Imagineability", "Intensity", "Letters", 
                                         "Meaning", "Modality", "Morphemes", "Name Agreement", 
                                         "Orthographic Neighborhood", "Part of Speech", 
                                         "Phonemes",
                                         "Phonographic Neighborhood", "Priming", "Pronunciation", 
                                         "Response Latency", "Recall", "Recognition", "Rime", 
                                         "Semantic", "Sensory", "Sentence Completion", "Similarity",
                                         "Syllables", "Syntax", "Typicality", 
                                         "Valence", "Visual Complexity", "Word Completion"))


ui <- fluidPage( #open ui
  sidebarLayout( #open fluid page and sidebar layout
  sidebarPanel( #open sidebarPanel
    
    selectInput("choice", "Choose a variable:", 
                choices = c("Stimuli", "Tags", "Journal", "Language"),
                selected = "Stimuli")
  ), #close sidebar Panel
  mainPanel( #open mainPanel
    dataTableOutput('freqtable')
  ) #close mainPanel
) # close sidebar Layout
) #close fluidpage

server <- function(input, output) {
  
  output$freqtable <- renderDataTable({
    
    if (input$choice == "Stimuli") {freqvalues = longtype$value}
    if (input$choice == "Tags") {freqvalues = longstimuli$variable}
    if (input$choice == "Journal") {freqvalues = tablemain$ref_journal}
    if (input$choice == "Language") {freqvalues = tablemain$language}
      
    tablef = count(freqvalues)
    tablef$percent = round(tablef$freq/sum(tablef$freq) * 100, 2)
    colnames(tablef) = c("Variable", "Frequency", "Percent")
    tablef
  })
}

shinyApp(ui, server, options = list(height = 550))
```

### View the Yearly Statistics

#### Stimuli Per Year

This app allows you to view the stimuli frequencies across years.

```{r stimuli_per_year, echo=FALSE}
#set up stimuli per year
table_stim = subset(overall_lab, select = c(STUFFID, type1, type2, year))
longtable = melt(table_stim, 
                 id = c("STUFFID", "year"), 
                 measured = c("type1", "type2"))

colnames(longtable)[3]="Type"

#To change the years from being factors
longtable$year = as.numeric(as.character(longtable$year))

##define ui
ui <- fluidPage(
  
  # Application title
  #titlePanel("Stimuli Frequency"),
  
  #Select Box
  sidebarPanel(
    
    selectInput(inputId = "select", 
                label ="Stimuli:", 
                choices = c(names(table(longtable$value)))), #close select
    helpText("This graphic indicates the publication frequency of 
              of each type of stimuli across years.",
             p(), "You can right click on the graphic to save it.") #close help
  ), #close sidebarpanel


  mainPanel(
    plotOutput("distPlot")
  ) #close main
) #close fluid

# Define server logic 
server <- function(input, output) {
  
  output$distPlot <- renderPlot({
    
    graphdata = subset(longtable, value == input$select)
    
    #bins <- (length.out = input$bins + 1)
    
    # draw the histogram with the specified number of bins
    ggplot(graphdata, aes(year)) + 
      geom_histogram(#binwidth = bins, 
                     color = "black", 
                     fill = "white") +
      xlab("Year") +
      ylab("Frequency") +
      cleanup 
  })
}

# Run the application 
shinyApp(ui, server, options = list(height = 450))
```

#### Tags Per Year

This app allows you to view the tag frequencies across years. 

```{r tag_per_year, echo=FALSE}
#set up tag per year
doom = overall_lab
doom$year2 = as.numeric(as.character(doom$year))

# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   #titlePanel("Tag Frequency"),
   
   # Sidebar with a slider input for number of bins 

      sidebarPanel(
         selectInput("choose",
                     "Tags:",
                     choices = list("Accuracy" = "accuracy",
                       "Age of Acquisition" = "aoa",
                       "Ambiguity" = "ambiguity",
                       "Arousal" = "arousal",
                       "Association" = "assoc",
                       "Categories" = "category",
                       "Cloze Probabilities" = "cloze",
                       "Complexity" = "complex",
                       "Concreteness" = "concrete",
                       "Confusion Matrices" = "confusion",
                       "Context" = "context", 
                       "Distinctivenes" = "sdist",
                       "Dominance" = "dominate",
                       "Ease of Learning" = "easelearn",
                       "Familiarity" = "familiar",
                       "Frequency" = "freq",
                       "Grapheme-Phoneme Correspondence" = "gpc",
                       "Indentification" = "identify",
                       "Image Agreement" = "imageagree",
                       "Image Variability" = "imagevar",
                       "Imaginability" = "imagine",
                       "Intensity" = "intense",
                       "Letters" = "letters",
                       "Lexical Decision" = "identifyld",
                       "Meaning" = "meaning",
                       "Modality" = "modality",
                       "Morphemes" = "morph",
                       "Name Agreement" = "nameagree",
                       "Naming" = "identifyn",
                       "Orthographic Neighborhood" = "orthon",
                       "Part of Speech" = "pos",
                       "Phonemes" = "phonemes",
                       "Phonographic Neighborhood" = "phonon",
                       "Priming" = "prime",
                       "Pronunciation" = "pronounce",
                       "Response Latency" = "rt",
                       "Recall" = "recall",
                       "Recognition" = "recognition",
                       "Rime" = "rime",
                       "Semantic" = "semantic",
                       "Sensory" = "sensory",
                       "Sentence Completion" = "sentcomp",
                       "Similarity" = "similar",
                       "Syllables" = "syllables",
                       "Syntax" = "syntax", 
                       "Typicality" = "typical",
                       "Valence" = "valence",
                       "Visual Complexity" = "visualcomp",
                       "Word Completion" = "wordcomp")),
          helpText("This graphic indicates the publication frequency of 
              normed information across years for tags.",
              p(), "You can right click on the graphic to save it.") #close help 
      ),
      
      # Show a plot of the generated distribution
      mainPanel(
         plotOutput("yearhist")
      )
   )


# Define server logic required to draw a histogram
server <- function(input, output) {
  
   output$yearhist <- renderPlot({
     #binsno <- (length.out = input$binsno + 1)
     
     graphdata = doom[ , c(input$choose, "year2")]
     colnames(graphdata) = c("picked", "year")
     graphdata = subset(graphdata, picked > 0)
     masterhist1 = ggplot(graphdata, aes(year))
     masterhist1 +
       geom_histogram(#binwidth = binsno, 
                      color = "black", 
                      fill = "white") +
       xlab("Year") + 
       ylab("Frequency") +
       cleanup +
       NULL
   })
}

# Run the application 
shinyApp(ui, server, options = list(height = 450))
```

#### Papers Per Year

This app allows you to view the number of papers published in each year. Please note that databases with no associated publication excluded from this chart.

```{r papers_per_year, echo=FALSE}
labtable2 = overall_lab

labtable2$year = as.numeric(as.character(labtable2$year))

# Define UI for application that draws a histogram
ui <- fluidPage(#open
  
  # Application title
  #titlePanel("Publication Frequency"),
   
  #Select Box
  sidebarPanel(
     
     sliderInput("year", 
                 label = "Year:",
                 min = 1910, max = 2018, value = c(1910, 2018),
                 sep = ""),
     helpText("This graphic indicates the publication frequency of 
              normed information across years. Please use the slider 
              bar to zoom into a specified year range.",
              p(), "You can right click on the graphic to save it.") #close help 
  ), #close sidebar panel
  
   # Show a plot of the generated distribution
   mainPanel(#open
     plotOutput("distPlot")
     )#close main Panel
  )#close fluid page
   

# Define server logic required to draw a histogram
server <- function(input, output) {
  
  output$distPlot <- renderPlot({
    
    graphdata = subset(labtable2, year >= input$year[1] & year <= input$year[2])
    
    # draw the histogram with the specified number of bins
    yearhist = ggplot(graphdata, aes(year))
    yearhist +
    geom_histogram(binwidth = 2, 
                   color = "black", 
                   fill = "white") +
    xlab("Year") + 
    ylab("Frequency") +
    cleanup
  })
}

# Run the application 
shinyApp(ui, server, options = list(height = 450))
```

